### 2020-12-04 fe_px_paper/fe_body_text.tex
Added extra Fe results discussion

\subsection{Measurement of nuclear excitation functions}

After irradiation, all foils were 
% confirmed to 
still sealed in their Kapton packets, verifying that no activation products were lost due to packet failure.
% and dispersal.
With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of 
% thermal swelling, 
off-gassing of oxides and the formation of gaseous short-lived beta activities in the tape.
% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
This blister   verifies that the primary proton beam was incident upon the foil, and provides additional 
% the first 
evidence 
% (before gamma-ray spectrometry) 
that the beam was stopped in the stack between Ti-20 and Cu-20.
% , producing a Bragg peak at this location.  
Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 17.9$~\pm~$1.0\,nAh 
% 18.8$\pm$1.0\,nAh
was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$~\pm~$1.3\,nAh using the linear fit model.
Similarly, for the 25\,MeV stack, a fluence of 27.5$~\pm~$8.3\,nAh 
% 33.2$\pm$4.7\,nAh
was calculated to be incident upon the 
% 55\,MeV 
target stack using the FLUKA fluence model, and a  fluence of 31.7$~\pm~$3.7\,nAh using the linear fit model to the four frontmost compartments (before the fluence loss becomes strongly nonlinear).
% 37.0$\pm$9.3\,nAh using the linear fit model.
% All of these 
Both linear models are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
% beamline 
current integrators.
However, for both target stacks, the FLUKA transport model predicts a significant increase in proton fluence, in particular for the 25\,MeV stack.
This model fails to reproduce the fluence loss seen in monitor foils, and predicts a significantly higher production of lower-energy secondary protons not seen in the activation data.
As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
This incident fluence dropped by approximately 
% 9.5\% to  17.0$\pm$2.4\,nAh (and by 
8.9\% to  17.3$~\pm~$1.5\,nAh using the linear fit model over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
This loss of fluence is due to a combination of 
% beam utilization for the various 
(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.

Using the final proton fluence at each energy position, cross sections for \ce{^{48,49,51}Cr}, \ce{^{48}V},  \ce{^{51,52m,52g,52,54,56}Mn},   \ce{^{52}Fe}, and \ce{^{55,56,57,58m,58g,58}Co}
 were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, presented in \autoref{tab:fe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57,60,61}Co},   and \ce{^{60,61,64}Cu}  were extracted, 
% as recorded 
presented in \autoref{tab:cufe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K} and \ce{^{44g,44m,44,47,48}Sc}  were extracted, 
% as recorded 
presented in \autoref{tab:ti_rp_table}.
In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are presented in \autoref{tab:fe_ibr_table}.
Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
% Appendices 
\ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).

@@

@@

These results have several notable features.
The 
% various 
\ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with 
% the body of measurements in the 
literature,  but have been measured nearly exclusively with the highest precision to date.
While (p,x) reactions below 70\,MeV on these elements are well-characterized overall, measurements of several reaction channels are somewhat sparse in comparison.
Indeed, fewer than four existing measurements have been performed for the \ce{^{nat}Fe}(p,x)\ce{^{48}Cr},\ce{^{52}Fe}, \ce{^{nat}Cu}(p,x)\ce{^{60}Cu},\ce{^{61}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44}Sc}
% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the 
reactions presented here.
% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
Additionally, \ce{^{22,24}Na} activity is seen in all foils, consistent with proton activation of the trace  silicon in the Kapton tape used for foil encapsulation, as described in our previous work\,\cite{Voyles2018a}.
No cross sections for \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.

% Furthermore, t
This work presents the first measurements of several observables in 
% these mass regions.
% This work reports the first experimental measurement of
this mass region, including the \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region, 
% It also represents  the first measurement of 
the independent cross sections for       \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).  
The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{51}Cr},\ce{^{52g}Mn},\ce{^{58g}Co} cross sections.
% Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
% (${^{1}/_{2}}^{-}$)
% ($\sfrac{1}{2}^-$) 
% isomer branching ratio via \ce{^{nat}Nb}(p,x).

Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target. 
It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life. 
Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20~\pm~0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section. 
Additionally, the \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} and \ce{^{nat}Fe}(p,x)\ce{^{56}Co} channels have a difference in apparent energetic thresholds of nearly 20\,MeV.
This provides some energy discrimination sensitivity in the same iron foil, particularly in the 20--50\,MeV region, which could be useful for determining incident proton energy near 40\,MeV, where fast neutrons are less significant than deeper in the stack.

Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reactions below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date. 
\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} appears to offer a compelling alternative to the more established \ce{^{50}Cr}(d,x)\ce{^{51}Mn} pathway, which necessitates an enriched \ce{^{50}Cr} target to avoid radio-manganese contamination from reactions on stable isotopes of Cr\,\cite{Klein2000}.
% However, 
\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} could be used for 
% clean 
production of  \ce{^{51}Mn} ($\geq$98.8\% radioisotopic purity) below 20\,MeV using the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} channel.
In addition, this low-energy production is accessible using the international network of small medical and research cyclotrons, enabling in-house production of this short-lived ($t_{1/2}=46.2~\pm~0.1$ m\,\cite{Wang2017}) radionuclide.
To increase yields over \ce{^{nat}Fe}(p,x), an enriched \ce{^{54}Fe} target could be used to take advantage of the eight-fold increase in reaction cross section for production using 40--50\,MeV protons, without opening the additional manganese exit channels accessible on a natural target.

Likewise, \ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
Conventional production uses the low-energy \ce{^{nat}Cr}/\ce{^{52}Cr}(p,n)\ce{^{52}Mn} pathways, which offer high radioisotopic purity (approximately 99.6\%)\,\cite{Graves2015,Wooten2015}.
\ce{^{nat}Fe}(p,x) offers a nearly threefold increase in production yield, but the low radioisotopic purity (99.1\% for 20--30\,MeV, decreasing to 60.8\% by 40\,MeV) at higher energies due to the opening of \ce{^{54}Mn} makes this route seem impractical.
Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn} and long-lived Co radiocontaminants, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$~\pm~$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in half-life, to avoid the unfavorable gammas produced by the isomer. 
However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$~\pm~$0.008\,h\,\cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator\,\cite{Blauenstein1997}.
Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.

In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
These include the non-standard positron emitters 
\ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
%\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
\ce{^{55}Co}\,\cite{Thisgaard2011,Zaman1996,Hermanne2000a}
\ce{^{61}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
\ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}
\ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
% \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
% \ce{^{89}Zr}\,\cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
% \ce{^{90}Nb}\,\cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
and the $\beta^-$-therapeutic agent 
\ce{^{47}Sc}\,\cite{Muller2014,Deilami-nezhad2016}.
% and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x). 
% The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co}\,\cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
% This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination\,\cite{MICHEL1997153,Ditrói2013}.
The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.

\subsection{Comparison of reaction modeling with experimental results}

@@

@@

The measured cross sections were compared to the predictions by the reaction codes TALYS, EMPIRE, CoH, ALICE, and by the calculations in the TENDL database.
The codes were all run on their default settings, in order to assess their predictive capabilities for the casual user.
The default settings for the optical models and gamma strength function ($\gamma$SF) are listed in  \autoref{tab:fe_defaults}.
The level density models for each are as follows.
For both CoH and TALYS, the default level density model is the Gilbert-Cameron (GC) model \cite{Gilbert2011}, which uses the Constant Temperature model at lower excitation energies and the Fermi Gas model at higher energies.
In EMPIRE, the default level density model is the Enhanced Generalized Superfluid Model (EGSM) \cite{Giardina2002}.
This model uses the Generalized Superfluid Model (GSM) \cite{ignatyuk1979role,Ignatyuk1993} at lower energies and the Fermi Gas model as well at higher energies, and has been normalized to discrete levels.
This normalization is performed in such a way that it only affects the level density below the neutron separation energy.
Finally, the default level density model in ALICE is the Kataria-Rarnamurthy-Kapoor (KRK) model \cite{Kataria1978,Kataria1990}, a semi-empirical nuclear level density formula which provides shell-dependent corrections to the nuclear mass surface, based on a Fourier expansion of the single particle level density of nucleons.

\begin{figure}[h]
 \centering
 \includegraphics[width=0.5\textwidth]{./figures/51Mn.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} cross section, with the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction channel visibly peaking at approximately \mbox{15 MeV}.}
 \label{fig:51Mn}
\end{figure}

\begin{figure}[h]
 \centering
 \includegraphics[width=0.5\textwidth]{./figures/52Mn.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
 \label{fig:temp_52Mn}
\end{figure}

>>>>

% \subsection{Measurement of nuclear excitation functions}

After irradiation, all foils were 
% confirmed to 
still sealed in their Kapton packets, verifying that no activation products were lost due to packet failure.
% and dispersal.
With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of 
% thermal swelling, 
off-gassing of oxides and the formation of gaseous short-lived beta activities in the tape.
% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
This blister   verifies that the primary proton beam was incident upon the foil, and provides additional 
% the first 
evidence 
% (before gamma-ray spectrometry) 
that the beam was stopped in the stack between Ti-20 and Cu-20.
% , producing a Bragg peak at this location.  
% Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 17.9$~\pm~$1.0\,nAh 
% % 18.8$\pm$1.0\,nAh
% was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$~\pm~$1.3\,nAh using the linear fit model.
% Similarly, for the 25\,MeV stack, a fluence of 27.5$~\pm~$8.3\,nAh 
% % 33.2$\pm$4.7\,nAh
% was calculated to be incident upon the 
% % 55\,MeV 
% target stack using the FLUKA fluence model, and a  fluence of 31.7$~\pm~$3.7\,nAh using the linear fit model to the four frontmost compartments (before the fluence loss becomes strongly nonlinear).
% % 37.0$\pm$9.3\,nAh using the linear fit model.
% % All of these 
% Both linear models are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
% % beamline 
% current integrators.
% However, for both target stacks, the FLUKA transport model predicts a significant increase in proton fluence, in particular for the 25\,MeV stack.
% This model fails to reproduce the fluence loss seen in monitor foils, and predicts a significantly higher production of lower-energy secondary protons not seen in the activation data.
% As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
% This incident fluence dropped by approximately 
% % 9.5\% to  17.0$\pm$2.4\,nAh (and by 
% 8.9\% to  17.3$~\pm~$1.5\,nAh using the linear fit model over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
% This loss of fluence is due to a combination of 
% % beam utilization for the various 
% (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.

Using the final proton fluence at each energy position, cross sections for \ce{^{48,49,51}Cr}, \ce{^{48}V},  \ce{^{51,52m,52g,52,54,56}Mn},   \ce{^{52}Fe}, and \ce{^{55,56,57,58m,58g,58}Co}
 were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, presented in \autoref{tab:fe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57,60,61}Co},   and \ce{^{60,61,64}Cu}  were extracted, 
% as recorded 
presented in \autoref{tab:cufe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K} and \ce{^{44g,44m,44,47,48}Sc}  were extracted, 
% as recorded 
presented in \autoref{tab:ti_rp_table}.
In addition, as there exist a number of isomers with 
% radioactive 
unstable ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are presented in \autoref{tab:fe_ibr_table}.
% Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
% % Appendices 
% \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).

@@

The measured cross sections were compared to the predictions by the reaction codes TALYS, EMPIRE, CoH, ALICE, and by the calculations in the TENDL database.
The codes were all explicitly run using their default parameters, for two primary motivations. 
First, this  assesses their claims of  predictive capabilities  --- many \enquote{casual} users (i.e., outside of data evaluation) will likely not make significant adjustments to the massively multi-parameter physics models used in these codes, nor should they need to, due to an expectation of reasonable accuracy in these results.
Indeed, TALYS and TENDL  are routinely used for modeling cross sections in initial target designs for isotope production applications.
Second, our recent work has shown that  arbitrary parameter optimization (tuning to provide a best fit to a single reaction channel)  often provides non-unique solutions, causing neighboring reaction channels (e.g., (p,4n) vs. (p,p3n)) to suffer \cite{fox2020investigating}.
Without a global physical basis for optimization (as in the process of reaction evaluation), an unchecked fit to experimental data offers no insight for reaction modeling, and may propagate to highly non-physical results for  competing channels.
% in order to assess their predictive capabilities for the casual user.
% The explicit use of default parameters was chosen for two reasons ---

The default settings for the optical models and gamma strength function ($\gamma$SF) are listed in  \autoref{tab:fe_defaults}.
The level density models for each are as follows.
For both CoH and TALYS, the default level density model is the Gilbert-Cameron (GC) model \cite{Gilbert2011}, which uses the Constant Temperature model at lower excitation energies and the Fermi Gas model at higher energies.
In EMPIRE, the default level density model is the Enhanced Generalized Superfluid Model (EGSM) \cite{Giardina2002}.
This model uses the Generalized Superfluid Model (GSM) \cite{ignatyuk1979role,Ignatyuk1993} at lower energies and the Fermi Gas model as well at higher energies, and has been normalized to discrete levels.
This normalization is performed in such a way that it only affects the level density below the neutron separation energy.
Finally, the default level density model in ALICE is the Kataria-Rarnamurthy-Kapoor (KRK) model \cite{Kataria1978,Kataria1990}, a semi-empirical nuclear level density formula which provides shell-dependent corrections to the nuclear mass surface, based on a Fourier expansion of the single particle level density of nucleons.
The use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, by propagating the difficulties inherent to modeling a wide number of reaction channels, to multiple target isotopes.
As a result, this analysis is useful for a qualitative comparison of default predictive capabilities, but no firm conclusions can be drawn about the direct causes of any inaccuracies, as there are many \enquote{moving parts} in these calculations.

@@

% \subsection{Comparison of reaction modeling with experimental results}

@@

These results have several notable features.
The 
% various 
\ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with 
% the body of measurements in the 
literature,  but have been measured nearly exclusively with the highest precision to date.
While (p,x) reactions below 70\,MeV on these elements are well-characterized overall, measurements of several reaction channels are somewhat sparse in comparison.
Indeed, fewer than four existing measurements have been performed for the \ce{^{nat}Fe}(p,x)\ce{^{48}Cr},\ce{^{52}Fe}, \ce{^{nat}Cu}(p,x)\ce{^{60}Cu},\ce{^{61}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44}Sc}
% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the 
reactions presented here.
% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
Additionally, \ce{^{22,24}Na} activity is seen in all foils, consistent with proton activation of the trace  silicon in the Kapton tape used for foil encapsulation, as described in our previous work\,\cite{Voyles2018a}.
No cross sections for \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
Discussion of notable reaction channels follows here, and 
comparisons  of the
remaining measured cross sections and isomer branching ratios with modeling results and literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
% Appendices 
\ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.

@@

% discussion should follow the pattern:
% short statements about the comparison to earlier work by channel, short statements
% 4about the agreement with models by channel; overall agreement to earlier data and to particular models.

\subsection{\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} cross section}

This work presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction in this energy region.
However, below the 24.1\,MeV threshold for \ce{^{56}Fe}(p,x)\ce{^{51}Mn}, the single measurement of \ce{^{54}Fe}(p,x)\ce{^{51}Mn} from Levkovski can be renormalized by isotopic abundance, and is consistent  with the present work \cite{levkovski1991cross}.
For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by EMPIRE, CoH and ALICE.
The higher-energy reactions on the higher mass Fe isotopes, however, are better matched by  EMPIRE and CoH.
ALICE overpredicts the production of \ce{^{51}Mn} in both peaks, and appears to peak at too high an energy.
As was seen in the modeling of high-energy proton-induced niobium reactions\,\cite{Voyles2018a}, TALYS and TENDL do well with the lower-energy \enquote{compound} reactions but do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
EMPIRE and CoH seem to accurately predict the locations of the peaks, but often fail to reliably estimate the magnitude of the cross section.

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{./figures/51Mn.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} cross section, with the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction channel visibly peaking at approximately \mbox{15 MeV}.}
 \label{fig:51Mn}
\end{figure}

\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} appears to offer a compelling alternative to the more established \ce{^{50}Cr}(d,x)\ce{^{51}Mn} pathway, which necessitates an enriched \ce{^{50}Cr} target to avoid radio-manganese contamination from reactions on stable isotopes of Cr\,\cite{Klein2000}.
% However, 
\ce{^{nat}Fe}(p,x)\ce{^{51}Mn} could be used for 
% clean 
production of  \ce{^{51}Mn} ($\geq$98.8\% radioisotopic purity) below 20\,MeV using the \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} channel.
In addition, this low-energy production is accessible using the international network of small medical and research cyclotrons, enabling in-house production of this short-lived ($t_{1/2}=46.2~\pm~0.1$ m\,\cite{Wang2017}) radionuclide.
To increase yields over \ce{^{nat}Fe}(p,x), an enriched \ce{^{54}Fe} target could be used to take advantage of the eight-fold increase in reaction cross section for production using 40--50\,MeV protons, without opening the additional manganese exit channels accessible on a natural target.

% discussion should follow the pattern:
% short statements about the comparison to earlier work by channel, short statements
% 4about the agreement with models by channel; overall agreement to earlier data and to particular models.

\subsection{\ce{^{nat}Fe}(p,x)\ce{^{52m,g}Mn} cross sections}

% \begin{figure}[h]
%  \centering
%  \includegraphics[width=0.5\textwidth]{./figures/52Mn.pdf}
%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
%  \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
%  \label{fig:temp_52Mn}
% \end{figure}

% \begin{figure}[h]
%  \centering
%  \includegraphics[width=0.5\textwidth]{./figures/52mMn.pdf}
%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
%  \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} cross section, with the \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52m}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52m}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.}
%  \label{fig:temp_52mMn}
% \end{figure}
